---
title: "hw5"
author: "Yutian Luo"
date: "11/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

# `Problem 1`

The Washington Post has gathered data on homicides in 50 large U.S. cities and made the data available through a GitHub repository here. You can read their accompanying article here.

```{r read homi data}

homi_data = 
  read.csv(file = "./data/homicide-data.csv")

```


Describe the raw data. Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

A:

The dataset has `r ncol(homi_data)` variables and `r nrow(homi_data)` rows. The importat variables include `r names(homi_data)`. 


```{r summarise homi data to homi_city}

# create city_state var
homi_data = 
  homi_data %>% 
  mutate(
    city_state = paste(city, ",",  state)
  ) 

# summaries
df1 = 
  homi_data %>% 
  group_by(city_state) %>% 
  summarise(total_homi = n())%>%
  arrange(desc(total_homi))

df2 = 
  homi_data %>% 
  filter(disposition %in%  c("Closed without arrest", "Open/No arrest")) %>% 
  group_by(city_state) %>% 
  summarise(num_unsolved = n()) %>% 
  arrange(desc(num_unsolved))

homi_city = 
full_join(df1, df2, by = "city_state")

```


For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r baltimore}

df_bal =
  homi_city %>% 
  filter(city_state ==  "Baltimore , MD") 

# store baltimore in tibble
lis_col_bal = 
  tibble(
    total = df_bal[[2]],
    unsolve = df_bal[[3]]
  )

# prop test
lis_col_balprop = 
      prop.test(x=lis_col_bal$unsolve, 
            n=lis_col_bal$total, 
            p = 0.5, 
            alternative = "two.sided", 
            conf.level = 0.95, 
            correct = TRUE) %>% 
      broom::tidy() 


# pull estimator and CI
lis_col_balprop %>% pull(estimate)
lis_col_balprop %>% pull(conf.low)
lis_col_balprop %>% pull(conf.high)

```


Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

```{r question}

homi_city = 
  homi_city %>% 
  drop_na()

lis_col_allcity = 
  tibble(
    total = homi_city[[2]],
    unsolve = homi_city[[3]]
  )

# map2(.x = lis_col_allcity$unsolve, 
#      .n = lis_col_allcity$total, 
#      .f = prop.test(lis_col_allcity$unsolve, lis_col_allcity$total, p = 0.5, "two.sided", conf.level = 0.95))

```



# `Problem 2`

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r read exp_data, include = FALSE}

# info for directions and file names
exp_df = 
  tibble(
    dir_base = "./data/data_2",
    filenames = list.files("./data/data_2"),
    dir_file = str_c(dir_base, sep = "/", filenames),
    res = vector("list", 20)
  ) %>% 
 
# read csv by map   
  mutate(
    exp = purrr::map(.x = dir_file, ~read_csv(file = .x))
  ) %>% 
  select(exp) %>% 
  unnest()

# tidy df, create vars necesary
exp_df = 
  exp_df %>% 
  mutate(
    subject_id = 1:20,
    con_arm = ifelse(subject_id == c(1:10), TRUE, FALSE)
  ) %>% 
  relocate(subject_id, con_arm)

```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r spaghetti plot}

exp_plot = 
  exp_df %>% 
  pivot_longer(
    cols = week_1:week_8,
    names_to = "weeks",
    values_to = "vals"
  ) %>% 

  ggplot(aes(x = weeks, y = vals, group = subject_id, color = con_arm)) +
  geom_line()

exp_plot
```

A:

At the start of the experiment, both groups are having similar values. For the experimental arm, as week time progress, the values are rising faster than the control arm. The experimental arm remains in a stable value inetrval during the 8 weeks.


# Problem 3

When designing an experiment or analysis, a common question is whether it is likely that a true effect will be detected – put differently, whether a false null hypothesis will be rejected. The probability that a false null hypothesis is rejected is referred to as power, and it depends on several factors, including: the sample size; the effect size; and the error variance. In this problem, you will conduct a simulation to explore power in a one-sample t-test.

First set the following design elements:

Fix n=30
Fix σ=5
Set μ=0
Generate 5000 datasets from the model

For each dataset, save μ̂
 and the p-value arising from a test of H:μ=0
 using α=0.05
. Hint: to obtain the estimate and p-value, use broom::tidy to clean the output of t.test.

```{r}

set.seed(1)

n = 30
sigma = 5
mu = 0

gen_norm = function(n, mu, sigma){
  tibble(
      rnorm(n = n, mean = mu, sd = sigma)
  )
}

resnorm_df = vector("list", 5000) 
for (i in 1:5000) {
     resnorm_df[i] = gen_norm(n, mu, sigma)
}

# compute mean and pvals
mu_pval = function(x){
  mean_x = t.test(x)$estimate
  pval_x = t.test(x)$p.value
  
  tibble(
    mean = mean_x,
    pval = pval_x
  )
}

# save mu and pval for each dataset
resnorm_mupval = map(resnorm_df, mu_pval)

```
























